---
title: "Weight of Fish"
author: "veronica gonzalez"
date: 11/1/2022  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
```

# Predicting Fish Weight


## Perch

```{r}
fish <- read.csv("Fish.csv")
Perch <- filter(fish, Species=="Perch")
Perch <- select (Perch,-Species)
```

```{r}
basicCN <- ggplot(Perch,aes(x=Weight,y=Length3))

basicCN + geom_point()+ geom_lm()
```




### Best Models



### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

The best regressive model are the height and the weight because of how their adjusted R2 is closr to 1  (0.9400). 

```{r}
perchmodel <- lm (Weight~ Height + Width, data= Perch)
summary.lm(perchmodel)
```

```{r}
pmodel <- lm (Weight~ Height + Width + Length1 + Length2+ Length3, data= Perch)
summary.lm(pmodel)
```

After comparing the three regression model with the two regressions model the summaries state that the two regression models have a lower residual standard error and a much higher adjusted R squared value.Stating that the best regression model is the one above. 

## bream

```{r}
fish <- read.csv("Fish.csv")
Bream <- filter(fish, Species=="Bream")
Bream <- select (Bream,-Species)
```

### Best Models

### Best Two regressor model
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Bream,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

The best two regression model in this chart is length 2 and the height that is higher up. The best three regression model is length one width and height. But the best regression model is definitely three. 

```{r}
Breammodel <- lm (Weight~ Height + Width, data= Bream)
summary.lm(Breammodel)
```

```{r}
pmodel <- lm (Weight~ Height + Width + Length1 + Length2+ Length3, data= Bream)
summary.lm(pmodel)
```

## Roach

```{r}
fish <- read.csv("Fish.csv")
Roach <- filter(fish, Species=="Roach")
Roach <- select (Roach,-Species)
```


### Best Models

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```
Our best one is the the length three width because the adjusted r2 is the highest compared to the others above. Because its the most closer to one 




```{r}
Roachmodel <- lm (Weight~ Height + Width, data= Roach)
summary.lm(Roachmodel)
```

```{r}
pmodel <- lm (Weight~ Width + Length3, data= Roach)
summary.lm(pmodel)
```


```{r}
favstats(Length1~ Weight,data=Perch)
```

```{r}
basicNN <- ggplot(Perch,aes(y=Weight,x=Length3))
basicNN + geom_point()+ geom_lm()
```

## Final Summary Statements





